Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-29 paper-ieee-trans.tex

A significant number of innovation projects and technology transfer
activities -- later discussed in Section~\ref{sec:ev} -- 
were funded by the 5th, 6th and 7th Framework Programmes of the European Commission (EC) 
and recently by the Horizon 2020 programme \cite{h2020}. Their main goal is to develop 
software solutions that provide a seamless and transparent access by researchers to 
distributed computing and data resources.

>>>>

A significant number of innovation projects and technology transfer
activities -- later discussed in Section~\ref{sec:ev} -- 
were funded by the 5th, 6th and 7th Framework Programmes of the European Commission (EC) 
and recently by the Horizon 2020 programme \cite{h2020}. Their main goal was to develop 
software solutions that provide a seamless and transparent access by researchers to 
distributed computing and data resources.
